Realizing Temporal Graphs

### 2023-01-26 RealizingTemporalGraphs.tex
Changes Wednesday 25th of January

@@

    We use the following subgraph $G_{i,j}$ as a \emph{edge selection gadget} for color combination $i,j$ with $i<j$. We first describe the vertex set of $G_{i,j}$.
    \begin{itemize}
        \item A set $X_{i,j}$ of vertices $x_1, x_2, \ldots, x_m$.
        \item A set $Y_{i,j}$ of vertices $y_1, y_2, \ldots, y_m$.
        \item A set $Z_{i,j}$ of vertices $z_1, z_2, \ldots, z_m$.
        \item Vertex sets $U_1, U_2, \ldots, U_m$ with $U_\ell=\{u^\ell_1, u^\ell_2,\ldots, u^\ell_n, u^\ell_{n+1}, u^\ell_{n+2}, u^v_{2n}\}$ for all $\ell\in[m]$. Let $U_{i,j}=\bigcup_{\ell\in[n]} U_\ell$.
        \item Two special vertices $v_{i,j}^\star,v_{i,j}^{\star\star}$.
    \end{itemize}
    Graph $G_{i,j}$ has the following edges.
    \begin{itemize}
        \item For all $\ell\in [m]$ we have edge $\{x_\ell,v_{i,j}^\star\}$, $\{y_\ell,v_{i,j}^\star\}$, and $\{z_\ell,v_{i,j}^{\star\star}\}$.

@@

    For each color $i$, we introduce the following vertices. Intuitively, what we describe in the following will be used as a \emph{verification gadget} for color $i$.
    \begin{itemize}
        \item We have $k-1$ vertices $v^i_\ell$ for $\ell\in[k]\setminus\{i\}$ and one vertex $v^i$.
        \item If $1\neq i\neq k$, then we have a set $\hat{U}_i$ of $n$ additional vertices $\hat{u}^i_1,\hat{u}^i_2,\ldots,\hat{u}^i_n$.
    \end{itemize}
    We add the following edges. Assume $1\neq i \neq k$. We describe the two cases $i=1$ and $i=k$ afterwards. Let $e_\ell\in F_{1,i}$ let $w^i_{\ell'}\in W_i$ be incident with $e_\ell$. Then we add edge $\{v^i,u^\ell_{\ell'}\}$ between $v^i$ and the vertex $u^\ell_{\ell'}$ of the edge selection gadget $G_{1,i}$.

    Let $1<j<i$ and let $e_\ell\in F_{j,i}$ let $w^i_{\ell'}\in W_i$ be incident with $e_\ell$. Then we add edge $\{v_{j-1}^i,u^\ell_{\ell'}\}$ between $v^i_{j-1}$ and the vertex $u^\ell_{\ell'}$ of the edge selection gadget $G_{j,i}$.
    Furthermore, we add edge $\{v_{j}^i,u^\ell_{\ell'+1}\}$ between $v^i_j$ and the vertex $u^\ell_{\ell'+1}$ of the edge selection gadget $G_{j,i}$.

@@

    Let $e_\ell\in F_{i,i+1}$ let $w^i_{\ell'}\in W_i$ be incident with $e_\ell$. Then we add edge $\{\hat{u}^i_n,u^\ell_{n+\ell'}\}$ between $\hat{u}^i_n$ and the vertex $u^\ell_{n+\ell'}$ of the edge selection gadget $G_{i,i+1}$.

    Let $i<j\le k$ and let $e_\ell\in F_{i,j}$ let $w^i_{\ell'}\in W_i$ be incident with $e_\ell$. Then we add edge $\{v_{j-1}^i,u^\ell_{n+\ell'}\}$ between $v^i_{j-1}$ and the vertex $u^\ell_{n+\ell'}$ of the edge selection gadget $G_{i,j}$.
    Furthermore, we add edge $\{v_{j}^i,u^\ell_{n+\ell'+1}\}$ between $v^i_j$ and the vertex $u^\ell_{n+\ell'+1}$ of the edge selection gadget $G_{i,j}$.

    Finally, we add two vertices $\hat{v},\hat{v}'$ and the following edges. Intuitively, what we describe next will be used to connect many vertex pairs by short paths, which will make arguing about possible labelings in yes-instances much easier.
    \begin{itemize}
        \item Edge $\{\hat{v},\hat{v}'\}$.
        \item An edge between $\hat{v}$ an all vertices in $X_{i,j}\cup Y_{i,j} \cup Z_{i,j}\cup U_{i,j}$ for all $1\le i<j\le k$.
        \item An edge between $\hat{v}'$ an all vertices in $X_{i,j}\cup Y_{i,j} \cup Z_{i,j}\cup U_{i,j}$ for all $1\le i<j\le k$.
    \end{itemize}
\end{proof}

@@

Similarly it holds if we want to include more vertices, that has to be visited by the path. If there is an edge (\ie a unique path) among two vertices, we denote it by $\rightarrow$,

@@

@@

    We want to guess the following fastest temporal paths
    $v_2 \rightarrow u \leadsto w \rightarrow z_2$,
    $v_2 \rightarrow u \leadsto z \rightarrow z_2$,
    $v_2 \rightarrow u \leadsto w \rightarrow z_{r-1}$ and
    $v_2 \rightarrow u \leadsto z \rightarrow z_{r-1}$.

@@

@@

In this section we study the properties of our problem, that then help us creating constraints of our ILP.
In our analysis we exploit the following greatly, that is why we state is as an observation.

@@

%From the above it follows that there are at most $O(|U|^2) = O(k^2)$ undetermined segments in $G'$ after the algorithm finishes with determining the labels for all fastest temporal paths among vertices of interest.
Now we want to relate the undetermined segments with the determined ones.
Let $S_{u,v}$ and $S_{w,z}$ be two segments.
At the beginning we have guessed what is a split vertex of a fixed vertex $v_i \in S_{u,v}$ in the segment  $S_{w,z}$. 
Denote this vertex as $z_j$, denote its neighbor closer to $w$ in $S_{w,z}$ as $z_{j-1}$,
and its neighbor closer to $z$ in $S_{w,z}$ as $z_{j+1}$.
We also guessed how the fastest temporal path from $v_i$ to $z_j$ starts and ends, which determined also the structure of the fastest temporal paths 
from $v_i$ to $z_{j-1}$ and from $v_i$ to $z_{j+1}$
(for the details see \cref{FPT:guess-splitFromAnotherSegmentAndPaths}).
W.l.o.g. assume that we have guessed that the fastest path from $v_i$ to $z_j$
passes through $w$ and $z_{j-1}$.
Then the fastest temporal path from $v_i$ to $z_{j+1}$ passes through $z$.
And all fastest temporal paths from $v_i$ to any $z_{j'} \in S_{w,z}$
use all of the edges in $S_{w,z}$ with the exception of the edge $z_j z_{j+1}$.
Using this information and \cref{obs:FirstLabelAndDuration}, we can determine the labels on all edges, with respect to the first or last label from the segment $S_{u,v}$,
with the exception of the edge $z_j z_{j+1}$.
Therefore all edges of $S_{w,z}$ but $z_j z_{j+1}$ become determined.
Since we repeat that procedure for all pairs of segments,
we get that for a fixed segment $S_{w,z}$ we end up with an undetermined edge $z_j z_{j+1}$
if and only if, this is an undetermined edge in relation to every other segment $S_{u,v}$ and its fixed vertex $v_i$.

@@

First we consider the case when $u,v$ are two vertices of interest.
This was the case that we partially studied at the beginning of the algorithm, that helped us determine certain labels of the graph.
We now iterate again through all fastest temporal paths from $u$ to $v$ and introduce an equality constraint for them.
We then continue 
through all of the paths from $u$ to $v$, and for every one, that is not the underlying path of a fastest temporal path, we add the inequality constraint.
There are $O(k^k)$ possible paths from $u$ to $v$ in $G'$, therefore in this step we introduce $O(k^{k^3})$ constraints.

Next we continue with the case of the fastest path from $u$ to $x$, where $u \in U$ and $x \in V(G') \setminus U$.
We have two possibilities:
\begin{enumerate}[(i)]
    \item Vertex $x$ is on a fastest temporal path from $u$ to some other vertex of interest $v$.
    Suppose that $x$ lies on a segment $S_{w,z}$.
    Then by \cref{claim:FPT-uv-LabelAlmostalledges} we know that the fastest temporal path from $u$ to $x$ is a subpath of the fastest temporal path from $u$ to $v$,
    which hast to be of the duration $D_{u,x}$. This results in adding an equality constraint to our ILP.
    We now have to iterate through all others temporal paths from $u$ to $x$ and add the constraint to ILP that states that their duration is not smaller than the value $D_{u,x}$.
    To reach $x$ from $u$, we have to first travel from $u$ to $w$ (resp.~$z$), and then travel through $S_{u,w}$ to $x$.
    There are $O(k^k)$ different paths to reach $w$ (resp.~$z$), which are then uniquely extended to $x$.
    Therefore we add $O(k^k)$ inequality constraints for all these paths.

@@

Now we proceed with the case of determining the fastest path from $x$ to $u$, where $x \in V(G') \setminus U$ and $u \in U$.
%We use the similar approach as in the case~\ref{item:FPT-uToxcase2} from above.
Let $x$ a vertex in the segment $S_{w,z} = (w,z_1,z_2, \dots, z_p, z)$.
We can easily determine the vertex $z_i \in S_{w,z}\setminus\{w,z\}$ for which the fastest temporal path from $z_i$ to $u$ has the biggest duration.
Denote this vertex as $z^*$. 
Then we know that all vertices in $S_{w,z}$ that are closer to $w$ than $z^*$ reach $u$ on the path that goes through $w$ and 
all the vertices in $S_{w,z}$ that are closer to $z$ than $z^*$ reach $u$ on the path that goes through $z$.
At the beginning we have also guessed the fastest path $z_1 \rightarrow w \rightarrow u$ (resp.~$z_p \rightarrow z \rightarrow u$).
Using this information we know all the fastest paths from any vertex in $S_{w,z} \setminus \{ z^* \}$ to $u$.
For all of these paths we introduce an equality constraint. 
For $z^*$ we have to determine which of the paths, through $w$ or $z$, to $u$ is the fastest.
Since we know the labels of all edges of $S_{w,z}$, with the exception of at most one edge, we can easily determine (procedure is similar as in Case~(\ref{item:FPT-uToxcase2}) from above),
which is the fastest temporal path from $z^*$ to $w$, which gives an equality constraint .
Now
we still need to add the inequality constraints for all other paths.
There are $O(k^k)$ paths between $w$ (resp.~$z$) and $u$, and a unique path from $z^*$ to $w$ (resp.~$z$).
For all paths from $w^*$ to $u$, that are not equal to the fastest, we introduce the inequality constraint.
This results in adding $O(k^k)$ inequality constraints.

Next is the case of determining the fastest path from $x$ to $y$, where $x,y \in V(G') \setminus U$.
Let $x$ be a vertex in the segment $S_{u,v} = (u,v_1,v_2, \dots, v_p, v)$ and let $y$ be a vertex in the segment $S_{w,z} = (w,z_1,z_3, \dots, z_r, z)$.
By checking the durations of the fastest paths from $x$ to every vertex in $S_{w,z} \setminus \{w,z\}$
we can determine the vertex $z_i \in S_{w,z} $, for which the duration from $x$ is the biggest.
This implies that the fastest temporal paths from $x$ to all vertices $z_1, z_2, \dots, z_{i-1}$ (resp.~$z_{i+1}, z_{i+2}, \dots, z_r$)  passes through $w$ (resp.~$z$).
Now we determine the vertex $z_j \in S_{u,v} \setminus \{u,v\}$,
for which the value of the durations of the fastest paths from it to the vertex $y$ is the biggest.
This implies that the fastest temporal paths from the vertices $v_1, v_2, \dots, v_{j-1}$ (resp.~$v_{j+1}, v_{j+2}, \dots, v_p$) to the vertex $y$ passes through $u$ (resp.~$v$).
At the beginning we have also guessed the following fastest paths  
$z_1 \rightarrow w \rightarrow u \rightarrow v_1$,
$z_1 \rightarrow w \rightarrow v \rightarrow v_p$,
$z_r \rightarrow z \rightarrow v \rightarrow v_p$ and
$z_r \rightarrow z \rightarrow v \rightarrow v_p$.
We distinguish following two cases,
first when $\{x,y\} \neq \{v_i, z_j\}$ and the second where $\{x,y\} = \{v_i, z_j\}$ (note this case encapsulates also the two cases when $x = v_i$ or $y=z_j$).
In the first case we know how the fastest temporal path from $x$ to $y$ exits the segment $S_{u,v}$ and enters the segment $S_{w,z}$.
Combining this with the guessed fastest paths, we uniquely determine the fastest temporal path from $x$ to $y$. 
For this path we add the equality constraint, and for all other paths (by similar arguing as in other cases there are $O(k^k)$ such paths) we add the inequality constraints.
In the second case when $\{x,y\} = \{v_i, z_j\}$ we do the following.
\todo{TODO}

>>>>

\sloppy

@@

    We will construct $G$ using several gadgets. We first introduce an \emph{edge selection gadget} for color combination $i,j$ with $i<j$. We start with describing the vertex set of the gadget.
    \begin{itemize}
        \item A set $X_{i,j}$ of vertices $x_1, x_2, \ldots, x_m$.
        \item A set $Y_{i,j}$ of vertices $y_1, y_2, \ldots, y_m$.
        \item A set $Z_{i,j}$ of vertices $z_1, z_2, \ldots, z_m$.
        \item Vertex sets $U_1, U_2, \ldots, U_m$ with $U_\ell=\{u^\ell_1, u^\ell_2,\ldots, u^\ell_n, u^\ell_{n+1}, u^\ell_{n+2}, u^v_{2n}\}$ for all $\ell\in[m]$. Let $U_{i,j}=\bigcup_{\ell\in[n]} U_\ell$.
        \item Two special vertices $v_{i,j}^\star,v_{i,j}^{\star\star}$.
    \end{itemize}
    The gadget has the following edges.
    \begin{itemize}
        \item For all $\ell\in [m]$ we have edge $\{x_\ell,v_{i,j}^\star\}$, $\{y_\ell,v_{i,j}^\star\}$, and $\{z_\ell,v_{i,j}^{\star\star}\}$.

@@

    For each color $i$, we introduce the following vertices. What we describe in the following will be used as a \emph{verification gadget} for color $i$.
    \begin{itemize}
        \item We have $k-1$ vertices $v^i_\ell$ for $\ell\in[k]\setminus\{i\}$ and one vertex $v^i_0$.
        \item If $1\neq i\neq k$, then we have a set $\hat{U}_i$ of $n$ additional vertices $\hat{u}^i_1,\hat{u}^i_2,\ldots,\hat{u}^i_n$.
    \end{itemize}
    We add the following edges. 
    %Assume $1\neq i \neq k$. We describe the two cases $i=1$ and $i=k$ afterwards. 
    If $i\neq 1$, let $e_\ell\in F_{1,i}$ let $w^i_{\ell'}\in W_i$ be incident with $e_\ell$. Then we add edge $\{v^i_0,u^\ell_{\ell'}\}$ between $v^i_0$ and the vertex $u^\ell_{\ell'}$ of the edge selection gadget of color combination $1,i$.

    Let $1<j<i$ (skip if $i=1$) and let $e_\ell\in F_{j,i}$ let $w^i_{\ell'}\in W_i$ be incident with $e_\ell$. Then we add edge $\{v_{j-1}^i,u^\ell_{\ell'}\}$ between $v^i_{j-1}$ and the vertex $u^\ell_{\ell'}$ of the edge selection gadget of color combination $j,i$.
    Furthermore, we add edge $\{v_{j}^i,u^\ell_{\ell'+1}\}$ between $v^i_j$ and the vertex $u^\ell_{\ell'+1}$ of the edge selection gadget of color combination $j,i$.

@@

    Let $e_\ell\in F_{i,i+1}$ let $w^i_{\ell'}\in W_i$ be incident with $e_\ell$. Then we add edge $\{\hat{u}^i_n,u^\ell_{n+\ell'}\}$ between $\hat{u}^i_n$ and the vertex $u^\ell_{n+\ell'}$ of the edge selection gadget of color combination $i,i+1$.

    Let $i<j\le k$ (skip if $i=k$) and let $e_\ell\in F_{i,j}$ let $w^i_{\ell'}\in W_i$ be incident with $e_\ell$. Then we add edge $\{v_{j-1}^i,u^\ell_{n+\ell'}\}$ between $v^i_{j-1}$ and the vertex $u^\ell_{n+\ell'}$ of the edge selection gadget of color combination $i,j$.
    Furthermore, we add edge $\{v_{j}^i,u^\ell_{n+\ell'+1}\}$ between $v^i_j$ and the vertex $u^\ell_{n+\ell'+1}$ of the edge selection gadget of color combination $i,j$.

    Next, we describe \emph{connector gadgets}. Intuitively, these gadgets will be used to connect many vertex pairs by short paths, which will make arguing about possible labelings in yes-instances much easier. Connector gadgets consist of three vertices $\hat{v}_0,\hat{v}_1,\hat{v}_2$. 
    %Each connector gadget is associated with four sets $A,A',B,B'$ containing vertices of other gadgets. 
    Each connector gadget is associated with two sets $A,B$ containing vertices of other gadgets. 
    Let $V^\star$ denote the set of all vertices from all edge selection gadgets and all validation gadgets.
    The sets $A$ and $B$ will only play a role when defining the distance matrix $D$ later. Informally speaking, vertices in $A$ should reach all vertices in $V^\star$ quickly through the gadget, except the ones in $B$.
    We have the following edges. 
    \begin{itemize}
        \item Edges $\{\hat{v}_0,\hat{v}_1\},\{\hat{v}_1,\hat{v}_2\}$.
        \item An edge between $\hat{v}_1$ and each vertex in $V^\star$.
        \item An edge between $\hat{v}_2$ and each vertex in $V^\star$.
    \end{itemize}
    We add two connector gadgets for each edge selection gadget and one connector gadget for each validation gadget.

    The first connector gadget for the edge selection gadget of color combination $i,j$ with $i<j$ has the following sets.
    \begin{itemize}
        \item Sets $A$ and $B$ contain all vertices in $X_{i,j}$ and vertex $v_{i,j}^{\star\star}$.
        %\item Set $A'$ contains all vertices from all edge selection gadgets and all validation gadgets except $X_{i,j}$.
        %\item Set $B$ contains all vertices from all edge selection gadgets and all validation gadgets, except $v_{i,j}^{\star\star}$.
        %\item Set $B$ contains vertex $v_{i,j}^{\star\star}$.
    \end{itemize}
    The second connector gadget for the edge selection gadget of color combination $i,j$ with $i<j$ has the following sets.
    \begin{itemize}
        \item Set $A$ contains all vertices from the edge selection gadget $G_{i,j}$ except vertices in $X_{i,j}$.
        %\item Set $A'$ contains all vertices in $X_{i,j}$.
        %\item Set $B$ contains all vertices from all edge selection gadgets and all validation gadgets.
        \item Set $B$ is empty.
    \end{itemize}

    The connector gadget for the verification gadget of color $i$ has the following sets.
    \begin{itemize}
        \item Sets $A$ and $B$ contain all vertices of the verification gadget and all vertices from edge selection gadgets that are neighbor of a vertex in the verification gadget.
    \end{itemize}

Lastly, we introduce an \emph{alignment gadget}. It consists of one vertex $w^\star$ and a set of vertices $\hat{W}$ containing one vertex for each edge selection gadget and one vertex for each connector gadget. Vertex $w^\star$ is connected to each vertex in $\hat{W}$.
The vertex $x_1$ of each edge selection gadget is connected to exactly one vertex in $\hat{W}$ and the vertex $\hat{v}_1$ of each connector gadget is connected to exactly one vertex in $\hat{W}$ such that all vertices in $\hat{W}$ have degree two.

This finished the description of the underlying graph $G$. We can observe that the vertex set containing
\begin{itemize}
    \item vertices $v_{i,j}^\star$ and $v_{i,j}^{\star\star}$ of each edge selection gadget,
    \item vertices $v^i_\ell$ with $\ell\in\{0,1,\ldots,i-1,i+1,\ldots,k\}$ and vertex $\hat{u}^i_n$ (if exists) of each validation gadget.
    \item vertices $\hat{v}_1$ and $\hat{v}_2$ of each connector gadget, and
    \item vertex $w^\star$ of the alignment gadget
\end{itemize}
forms a feedback vertex set in $G$ with size $O(k^2)$.

We proceed with describing the distance matrix $D$. We use the notation $d(v,v'):= D_{v,v'}$. For all vertices $v,v'$ that are neighbors in $G$ we have that $d(v,v')=1$ and $d(v',v)=1$.

Next, consider a connector gadget consisting of vertices $\hat{v}_0,\hat{v}_1,\hat{v}_2$ and with sets $A$ and $B$. Informally, the connector gadget makes sure that all vertices in $A$ can reach all other vertices (of edge selection gadgets and validation gadgets) except the ones in $B$. We set the following distances. Recall that $V^\star$ denotes the set of all vertices from all edge selection gadgets and all validation gadgets.
\begin{itemize}
    \item We set $d(\hat{v}_0,\hat{v}_1)=2$, $d(\hat{v}_1,\hat{v}_2)=2$, and $d(\hat{v}_0,\hat{v}_2)=3$.
    \item Let $v\in V^\star\setminus B$, then we set $d(\hat{v}_0,v)=3$.
    \item Let $v\in A$ and $v'\in V^\star\setminus B$ such that $v$ and $v'$ are not neighbors, then we set $d(v,v')=3$.
\end{itemize}

Next, consider the edge selection gadget for color combination $i,j$ with $i<j$.
\end{proof}

@@

Similarly it holds if we want to include more vertices that have to be visited by the path. If there is an edge (\ie a unique path) among two vertices, we denote it by $\rightarrow$,

@@

\begin{enumerate}[G-1.]

@@

    We want to guess the following fastest temporal path
    $v_2 \rightarrow u \leadsto w \rightarrow z_2$. 

@@

    Recall that $S_{u,v}\neq S_{v,u}$ for every $u,v\in U$. Furthermore note that we did not assume that the sets $\{u,v\}$ and $\{w,z\}$ are disjoint. Therefore, by repeatedly making the above guesses, we also guess the following fastest temporal paths: 
    ${v_2 \rightarrow u \leadsto z \rightarrow z_{r-1}}$,\ \ \ 
    ${v_2 \rightarrow u \leadsto v \rightarrow v_{p-1}}$,\ \ \  
    ${v_{p-1} \rightarrow v \leadsto w \rightarrow z_{2}}$,\ \ \  
    ${v_{p-1} \rightarrow v \leadsto z \rightarrow z_{r-1}}$, and  
    ${v_{p-1} \rightarrow v \leadsto u \rightarrow v_{2}}$.

@@

In this section we study the properties of our problem, that then help us creating constraints of our ILP.
Remember, with $G$ we denote our underlying graph of $D$. We want to determine labeling $\lambda$ of each edge of $G$.
We start with an empty labeling of edges and start adding certain values to them.
Note, these values are not (necessarily) numbers. 
In fact at the beginning the values will be determined with respect to each other (\ie as a function of each other).
In our analysis we exploit the following greatly, that is why we state is as an observation.

@@

%From the above it follows that there are at most $O(|U|^2) = O(k^2)$ undetermined segments in $G'$ after the algorithm finishes with determining the labels for all fastest temporal paths among vertices of interest.
Now we want to relate the undetermined segments with the determined ones.
Let $S_{u,v}$ and $S_{w,z}$ be two segments.
At the beginning we have guessed what is a split vertex of a fixed vertex $v_i \in S_{u,v}$ in the segment $S_{w,z}$. 
Denote this vertex as $z_j$, denote its neighbor closer to $w$ in $S_{w,z}$ as $z_{j-1}$,
and its neighbor closer to $z$ in $S_{w,z}$ as $z_{j+1}$.
We also guessed how the fastest temporal path from $v_i$ to $z_j$ starts and ends, which determined also the structure of the fastest temporal paths 
from $v_i$ to $z_{j-1}$ and from $v_i$ to $z_{j+1}$
(for the details see guess G-\ref{FPT:guess-splitFromAnotherSegmentAndPaths}). \todo{Two cases.}
W.l.o.g. assume that we have guessed that the fastest path from $v_i$ to $z_j$
passes through $w$ and $z_{j-1}$.
Then the fastest temporal path from $v_i$ to $z_{j+1}$ passes through $z$.
And all fastest temporal paths from $v_i$ to any $z_{j'} \in S_{w,z}$
use all of the edges in $S_{w,z}$ with the exception of the edge $z_j z_{j+1}$.
Using this information and \cref{obs:FirstLabelAndDuration}, we can determine the labels on all edges, with respect to the first or last label from the segment $S_{u,v}$,
with the exception of the edge $z_j z_{j+1}$.
Therefore, all edges of $S_{w,z}$ but $z_j z_{j+1}$ become determined.
Since we repeat that procedure for all pairs of segments,
we get that for a fixed segment $S_{w,z}$ we end up with an undetermined edge $z_j z_{j+1}$
if and only if, this is an undetermined edge in relation to every other segment $S_{u,v}$ and its fixed vertex $v_i$.

@@

\subsubsection*{\boldmath Fastest paths among $u,v$ where $u \in U$ and $v \in V$}
First we consider the case when $u,v$ are two vertices of interest.
This was the case that we partially studied at the beginning of the algorithm, that helped us determine certain labels of the graph.
We now iterate again through all fastest temporal paths from $u$ to $v$ and introduce an equality constraint for them.
We then continue 
through all of the paths from $u$ to $v$, and for every one, that is not the underlying path of a fastest temporal path, we add the inequality constraint.
There are $O(k^k)$ possible paths from $u$ to $v$ in $G'$, therefore in this step we introduce $O(k^{k^3})$ constraints.

\subsubsection*{\boldmath Fastest paths among $u,x$ where $u \in U$ and $x \in V(G') \setminus U$}
Next we continue with the case of the fastest path from $u$ to $x$, where $u \in U$ and $x \in V(G') \setminus U$.
We have three possibilities:
\begin{enumerate}[(i)]
    \item Vertex $x$ is on a segment $S_{u,v}=(u,v_1,v_2,\dots,v_p,v)$. 
    If $x$ is on a fastest path from $u$ to some other vertex, then we know that the fastest path from $u$ to $x$ travels along the $S_{u,v}$.
    Suppose now that the segment $S_{u,v}$ is not a part of a fastest path from $u$ to some other vertex.
    Denote with $P$ the underlying path of the fastest temporal path from $u$ to $v$, 
    and with $Q$ the fastest temporal path of form $u \leadsto v \rightarrow v_p$ (which we know as we have guessed it).
    We find the vertices $v_i, v_{i'} \in S_{u,v}$ that are on the furthest distance from $u$.
    Note that these two vertices are either neighbors, or the same vertex, \ie $i' \in \{i, i+1\}$.
    Then we know that the fastest temporal paths from $u$ to $v_1 v_2, \dots, v_{i-1}$ travel along $S_{u,v}$,
    and the fastest temporal paths from $u$ to $v_p, v_{p-1}, \dots, $.
    \todo{Missing}
    \item Vertex $x$ is on a fastest temporal path from $u$ to some other vertex of interest $v$.
    Suppose that $x$ lies on a segment $S_{w,z}$.
    Then by \cref{claim:FPT-uv-LabelAlmostalledges} we know that the fastest temporal path from $u$ to $x$ is a subpath of the fastest temporal path from $u$ to $v$,
    which hast to be of the duration $D_{u,x}$. This results in adding an equality constraint to our ILP.
    We now have to iterate through all others temporal paths from $u$ to $x$ and add the constraint to ILP that states that their duration is not smaller than the value $D_{u,x}$.
    To reach $x$ from $u$, we have to first travel from $u$ to $w$ (resp.~$z$), and then travel through $S_{u,w}$ to $x$.
    There are $O(k^k)$ different paths to reach $w$ (resp.~$z$), which are then uniquely extended to $x$.
    Therefore we add $O(k^k)$ inequality constraints for all these paths.

@@

Now we proceed with the case of determining the fastest path from $x$ to $u$, where $x \in V(G') \setminus U$ and $u \in U$.
%We use the similar approach as in the case~\ref{item:FPT-uToxcase2} from above.
Let $x$ a vertex in the segment $S_{w,z} = (w,z_1,z_2, \dots, z_p, z)$.
We can easily determine the vertex $z_i \in S_{w,z}\setminus\{w,z\}$ for which the fastest temporal path from $z_i$ to $u$ has the biggest duration.
Denote this vertex as $z^*$. 
Then we know that all vertices in $S_{w,z}$ that are closer to $w$ than $z^*$ reach $u$ on the path that goes through $w$ and 
all the vertices in $S_{w,z}$ that are closer to $z$ than $z^*$ reach $u$ on the path that goes through $z$.
At the beginning we have also guessed the fastest path $z_1 \rightarrow w \leadsto u$ (resp.~$z_p \rightarrow z \leadsto u$).
Using this information we know all the fastest paths from any vertex in $S_{w,z} \setminus \{ z^* \}$ to $u$.
For all of these paths we introduce an equality constraint. 
For $z^*$ we have to determine which of the paths, through $w$ or $z$, to $u$ is the fastest.
Since we know the labels of all edges of $S_{w,z}$, with the exception of at most one edge, we can easily determine (procedure is similar as in Case~(\ref{item:FPT-uToxcase2}) from above),
which is the fastest temporal path from $z^*$ to $w$, which gives an equality constraint .
Now
we still need to add the inequality constraints for all other paths.
There are $O(k^k)$ paths between $w$ (resp.~$z$) and $u$, and a unique path from $z^*$ to $w$ (resp.~$z$).
For all paths from $w^*$ to $u$, that are not equal to the fastest, we introduce the inequality constraint.
This results in adding $O(k^k)$ inequality constraints.

\subsubsection*{\boldmath Fastest paths among $x,y$ where $x \in V(G') \setminus U$ and $y \in V(G') \setminus U$}
Next is the case of determining the fastest path from $x$ to $y$, where $x,y \in V(G') \setminus U$.
We have two options.
\begin{enumerate}[(i)]
    \item Vertices $x,y$ are in the same segment $S_{u,v} = (u,v_1,v_2, \dots, v_p, v)$. W.l.o.g. suppose that $x$ is closer to $u$ in $S_{u,v}$ than $y$.
    Denote with $x = v_i$ and $y = v_j$, where $i < j$.
    Let $v_k \in S_{u,v}$ be a vertex for which the distance from $v_i$ is the biggest.
    Then we know that $D_{x,v_{i+1}} < D_{x,v_{i+2}} < \cdots  < D_{x,v_{k}}$ and $D_{x,v_{i-1}} < D_{x,v_{i-2}} < \cdots  < D_{x,v_{k}}$, where indices are taken modulo $p$.
    Then we know exactly the structure of all the fastest paths from $x$ to every vertex in $S_{u,v}$,
    with the exception of path $x \leadsto v_k$.
    \todo{Details}
    \item Vertices $x$ and $y$ are in different segments. 
Let $x$ be a vertex in the segment $S_{u,v} = (u,v_1,v_2, \dots, v_p, v)$ and let $y$ be a vertex in the segment $S_{w,z} = (w,z_1,z_3, \dots, z_r, z)$.
By checking the durations of the fastest paths from $x$ to every vertex in $S_{w,z} \setminus \{w,z\}$
we can determine the vertex $z_i \in S_{w,z} $, for which the duration from $x$ is the biggest.
This implies that the fastest temporal paths from $x$ to all vertices $z_1, z_2, \dots, z_{i-1}$ (resp.~$z_{i+1}, z_{i+2}, \dots, z_r$)  passes through $w$ (resp.~$z$).
Now we determine the vertex $z_j \in S_{u,v} \setminus \{u,v\}$,
for which the value of the durations of the fastest paths from it to the vertex $y$ is the biggest.
This implies that the fastest temporal paths from the vertices $v_1, v_2, \dots, v_{j-1}$ (resp.~$v_{j+1}, v_{j+2}, \dots, v_p$) to the vertex $y$ passes through $u$ (resp.~$v$).
At the beginning we have also guessed the following fastest paths  
$z_1 \rightarrow w \leadsto u \rightarrow v_1$,
$z_1 \rightarrow w \leadsto v \rightarrow v_p$,
$z_r \rightarrow z \leadsto v \rightarrow v_p$ and
$z_r \rightarrow z \leadsto v \rightarrow v_p$.
We distinguish following two cases,
first when $\{x,y\} \neq \{v_i, z_j\}$ and the second where $\{x,y\} = \{v_i, z_j\}$ (note this case encapsulates also the two cases when $x = v_i$ or $y=z_j$).
In the first case we know how the fastest temporal path from $x$ to $y$ exits the segment $S_{u,v}$ and enters the segment $S_{w,z}$.
Combining this with the guessed fastest paths, we uniquely determine the fastest temporal path from $x$ to $y$. 
For this path we add the equality constraint, and for all other paths (by similar arguing as in other cases there are $O(k^k)$ such paths) we add the inequality constraints.
In the second case when $\{x,y\} = \{v_i, z_j\}$ we do the following.
\todo{TODO}
\end{enumerate}

\subsubsection*{\boldmath Considering the paths for vertices from $Z$}
All of the above is enough to determine the labeling $\lambda$ of $G'$. Now we have to make sure that the labeling considers also the vertices in $Z$ that we initially removed from $G$.
Remember that removed vertices form disjoint trees in $G$.
Let us denote $Z$ as the set of disjoint trees, \ie $Z = T_1 \cup T_2 \cup \cdots \cup T_t$, where $T_i$ represents one of the trees.
Since there is a unique (static) path between any two vertices $t_1, t_2$ in a tree $T_i$,
it follows that there is also a unique (therefore also the fastest) temporal path among them.
Thus determining the label of an edge in $T_i$ uniquely determines the labels on all other edges of tree $T_i$.
Let us describe now how to determine the labels on edges of an arbitrary $T_i \in Z$.
For a tree $T_i$ denote with $u_i$ the vertex in $G'$ that is a neighbor of some vertex in $T_i$, 
call it a \emph{clip vertex of the tree $T_i$}
and denote with $r_i$ the neighbor of $u_i$, \ie the root of the tree $T_i$.
By construction (by iteratively removing vertices of degree one from $G$) it follows that there can be many different trees $T_i$ that are incident to the same clip vertex $u_i \in V(G')$,
but each tree $T_i$ is incident to exactly one clip vertex $u_i \in V(G')$.
First observe that $|N_{G'}(u_i)|\geq 1$, if not also $u_i$ would be removed from $G$.
To determine the correct label of all edges of $T_i$ we use the following property.
\begin{claim}
Let $T_i$ be a tree in $Z$ and let $e_i = (u_i,r_i)$ be an edge in $G$, where $u_i \in V(G')$ is a clip vertex of $T_i$ and $r_i \in T_i$ is a root of $T_i$.
Let $v \in N_{G'}(u_i)$ be the closest vertex to $r_i$, regarding the values of $D$, \ie  $D_{r_i,v} \leq D_{r_i,w}$ for all $w \in N_{G'}(u)$.
Then the path $P^*=(r_i,u_i,v)$ has to be the fastest temporal path from $r_i$ to $v$ in $G$.
\end{claim}
\begin{proof}
Suppose that this is not true.
Then there exists a faster path $P^*_2$ from $r_i$ to $v$, that goes through the clip vertex $u_i$ of $T_i$ (as this is the only neighbor of $r_i$), through some other vertex $w \in N_{G'}(u) \setminus \{v \}$, 
and through some other path $P'$ in $G$, before it finishes in $v$, where $P'$ is at least an edge (from $w$ to $v$). 
Therefore $P^*_2= (r_i,u_i,w,P',v)$, where $d(P^*_2) \leq d(P^*)$.
Now since $D_{r_i,v} \leq D_{r_i,w}$ for all $ w\in N_{G'}(u)$ the first part of path $P^*_2$ from $r_i$ to $w$ takes at least $D_{r_i,v}$ time.
Since $v \neq w$ we need at least one more time-step (one more edge) to traverse from $w$ to reach $v$. 
So $d(P^*_2) \geq D_{r_i,v} + 1$, and so $P^*_2$ cannot be faster than $P^*$.
\end{proof}
